\section{Literature Review}

Departmental Stores is {\em one spot shopping}. It is widely acceptable and
fast gaining business also known as Universal Suppliers.

Unlike online virtual store, in departmental stores, the items required by
every family are available under a single roof. Departmental stores specializes
in satisfying a wide range of goods and products of the consumers and
residential needs and at the same time offering them a choice of multiple
services at variable price points. It avoids the need to visit different places
to purchase different kinds of products from several places.

A typical Departmental Stores have following criteria for betterment of service
to public:
\begin{itemize}[noitemsep,topsep=0pt]
  \item Individual department are established as per different types of goods
    to be sold.
  \item Each Department is an independent unit ie. the sections operates
    independently under single management.
  \item Departmental Stores provides maximum shopping convenience to its
    customers.
  \item It keeps huge stock of fresh goods which highlight latest fashions and
    trends followed by different manufacturers.
\end{itemize}

The main aim of every departmental store is to provide and fulfill all
requirements of their customers at one place along with comforts and
facilities, which a small scale retailer cannot provide.

Buying, Supervision, accounting, advertising and external communications are
the basic operations of Departmental Stores handled directly by the central
management of the store. Imagine handling all the Accounting, Supervision,
Communications operated by the staffs, which is very monotonous for day to day
operations of the stores.

To avoid these tedious tasks, a software system could be employed to take over
these task of Accounting as Cashier, Supervise the stock as Supervisor, making
the deal with all Suppliers. Cashier making bills manually for the goods
purchased is a traditional approach which is outfit for modern departmental
stores to handle large customers and services.

On the other hand to keep daily record of stock available for each products
under all categories is almost impossible for any operators. Hence via this
software system, it could keep the daily track of the goods (products) sold and
the new arrival of goods from the suppliers so that there is surplus inventory
to avoid being ``out of stock'' at the time of purchase.
